Scikit-learn: machine learning without learning the machinery

### 2014-05-21 article.tex
Compress a but more the code

\begin{lstlisting}
>>> clf.predict_proba(["This movie is the worst I ever saw.",
...                    "Shawshank Redemption, eat your heart out!"])
array([[  9.99293000e-01,   7.07000280e-04],
       [  1.68757754e-01,   8.31242246e-01]])
\end{lstlisting}

@@

\begin{lstlisting}
>>> from sklearn.cross_validation import cross_val_score
>>> score = cross_val_score(clf, data.data, data.target, cv=5)
>>> score
array([ 0.91  ,  0.8825,  0.88  ,  0.8775,  0.86  ])
>>> score.mean()
0.88200000000000001
\end{lstlisting}

>>>>

\begin{lstlisting}
>>> clf.predict(["Worst movie I ever saw",
...      "Godzilla, eat your heart out!"])
array([0, 1])
\end{lstlisting}

@@

\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([ 0.91, 0.8825, 0.88, 0.8775, 0.86])
\end{lstlisting}
